### 2016-09-20 thesis/methods/methods.tex
tmp commit

%TODO: add data/sample composition -- ethinicity, grade, etc -- maybe in table form

The raw microarray gene expression data files of all 103 samples from the \citet{Creighton2012} study were downloaded from the \gls{geo} database (\gls{geo} accession ID: GSE24185).
Clinical data of the samples were obtained from the supplementary table 1 from \citet{Creighton2012} paper.
799 obesity associated gene probes identified in the \citet{Creighton2012} study were obtained from the supplementary data file 1 from \citet{Creighton2012} paper.
The raw expression data, clinical data, and the list of gene probes were imported into \gls{r}/RStudio.

@@

%TODO: add data/sample composition -- ethinicity, grade, etc -- maybe in table form
%TODO: find out where  the genes were taken from

The raw microarray gene expression data files of all *** samples from the  \citet{Fuentes-Mattei2014} study were downloaded from the \gls{geo} database (include website name/GEO ID here).
Clinical data for the samples in this study was not available.
130 obesity associated gene probes identified by \citet{Fuentes-Mattei2014} were downloaded from (supplementary data??).
The raw expression data and the list of gene probes were imported into \gls{r}/RStudio.

@@

%TODO: add data/sample composition -- ethinicity, grade, etc -- maybe in table form
%TODO: find out where  the genes were taken from
%TODO: Change Fuentes-Mattei citation to Cris Print's citation

The raw microarray gene expression data files of all *** samples from the  Print et al. study were downloaded from the \gls{geo} database (include website name/GEO ID here).
Clinical data for the samples in this study was not available.
*** obesity associated gene probes identified by Print et al. were downloaded from (supplementary data??).
The raw expression data and the list of gene probes were imported into \gls{r}/RStudio.

%TODO: add data/sample composition -- ethinicity, grade, etc -- maybe in table form
%TODO: find out where  the genes were taken from
%TODO: Change Fuentes-Mattei citation to Cris Print's citation

The raw microarray gene expression data files used in  \citet{Gatza2010a} study were downloaded from the \gls{geo} database (include website name/GEO ID here).
Only the Affymetrix HGU133A microarray samples were included in the project.
Clinical data for the samples in this study was not available.
*** obesity associated gene probes identified by \citet{Gatza2010a} were downloaded from (supplementary data??).
The raw expression data and the list of gene probes were imported into \gls{r}/RStudio.

@@

%TODO: May need more details on the sample (bmi status, etc.)
\begin{table}[h]
	\caption{Summary of the total number of samples included in the analyses for each cancer type}
	\label{tab:samplesize}
	\begin{center}
		\begin{tabular}{cc}
			\textbf{Cancer Type}   & \textbf{Total} \\
			\hline
			\rule{0pt}{2.25ex}BLCA & 261   \\
			CESC                   & 224   \\
			COAD                   & 226   \\
			KIRP                   & 124   \\
			LIHC                   & 264   \\
			READ                   & 73    \\
			SKCM                   & 218   \\
			UCEC                   & 482   \\
		\end{tabular}
	\end{center}
\end{table}

>>>>

The raw microarray gene expression data files from the \citet{Creighton2012} study were downloaded from the \gls{geo} database (\gls{geo} accession ID: GSE24185).
Clinical data of the samples were obtained from the supplementary table 1 from \citet{Creighton2012} paper.
799 obesity associated gene probes identified in the \citet{Creighton2012} study were obtained from the supplementary data file 1 from \citet{Creighton2012} paper.
The raw expression data, clinical data, and the list of gene probes were imported into \gls{r}.

@@

The raw microarray gene expression data files from the  \citet{Fuentes-Mattei2014} study were downloaded from the \gls{geo} database (\gls{geo} accession ID: GSE20194).
Clinical data for the samples in this study was also downloaded from the \gls{geo} database (same \gls{geo} accession ID).
130 obesity associated gene probes identified by \citet{Fuentes-Mattei2014} were taken from the supplementary table 3.
The raw expression data and the list of gene probes were imported into \gls{r}.

The raw microarray gene expression data files from the \citet{Gatza2010a} study were downloaded from the \gls{geo} database (\gls{geo} accession ID: GSE1456, GSE1561, GSE2034, GSE3494, GSE4922, and GSE6596).
Only the Affymetrix HGU133A microarray samples were included in the project.
Clinical data for the samples in this study was not available.
The raw expression data and the list of gene probes were imported into \gls{r}.

@@

%TODO: Find Cris's paper

The raw microarray gene expression data files from the  Print et al. study were downloaded from the \gls{geo} database (\gls{geo} accession ID: GSE36771).
Clinical data for the samples in this study was ******.
The raw expression data and the list of gene probes were imported into \gls{r}.

% TODO: Overall summary table of the samples from each data set at the end of this section.

@@

%TODO: May need more details on the sample (bmi status, etc.)
\begin{table}[h]
	\caption{Summary of the total number of samples included in the analyses for each cancer type}
	\label{tab:samplesize}
	\begin{center}
		\begin{tabular}{cc}
			\textbf{Cancer Type}   & \textbf{Total number of samples} \\
			\hline
			\rule{0pt}{2.25ex}BLCA & 261   \\
			CESC                   & 224   \\
			COAD                   & 226   \\
			KIRP                   & 124   \\
			LIHC                   & 264   \\
			READ                   & 73    \\
			SKCM                   & 218   \\
			UCEC                   & 482   \\
		\end{tabular}
	\end{center}
\end{table}
